Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/discussion.tex
Add FIXME for non-observable discussion

\paragraph{Causal Models with Non-Observable Variables}
We have assumed through this paper that all variables in the causal model were observable after an intervention is made.
A natural generalisation of our model would be for some variables to be unobservable.
\todom{More to say here?}
If the conditional models are known then the $Z_a$ terms in Algorithm~\ref{alg:general} could still be obtained via marginalising.
However, if this is not the case the estimation problem becomes more difficult.
% In this case, some conditional distributions may be non-identifiable. 
% The corresponding actions can be immediately added to the set $A$ prior to collecting any data. 
% We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data.
% Combining our estimation techniques with insights from \citet{Bareinboim2015} for handling unobserved confounders would be worth investigation.

>>>>

\paragraph{Causal Models with Non-Observable Variables}
We have assumed through this paper that all variables in the causal model were observable after an intervention is made.
A natural generalisation of our model would be for some variables to be unobservable.
\todom{FIX ME!}
If the conditional models are known then the $Z_a$ terms in Algorithm~\ref{alg:general} could still be obtained via marginalising.
However, if this is not the case the estimation problem becomes more difficult.
% In this case, some conditional distributions may be non-identifiable. 
% The corresponding actions can be immediately added to the set $A$ prior to collecting any data. 
% We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data.
% Combining our estimation techniques with insights from \citet{Bareinboim2015} for handling unobserved confounders would be worth investigation.
